\section{FUTURE WORK}

Definitively proving or disproving the existence of negative energy remains a captivating scientific challenge. 
The research presented here lays the groundwork for future endeavors aimed at unraveling this fundamental mystery. 
By pursuing these avenues of research, we can gain a deeper understanding of the nature 
of vacuum energy and its potential implications for our understanding of the universe.

Here are some potential avenues for future research:
\subsection*{Experimental Verification} 
    Continued advancements in experimental techniques might allow for the direct observation 
    or measurement of negative energy phenomena. 
    One potential approach could involve manipulating material properties or utilizing extreme environments 
    to create conditions conducive to negative energy states.
\subsection*{Theoretical Frameworks} 
    Further theoretical investigations could delve deeper into the nature of negative energy and 
    its compatibility with existing physical laws. 
    Exploring alternative interpretations of quantum field theory or developing new theoretical 
    frameworks might shed light on the possible existence and implications of negative energy.
\subsection*{Cosmological Implications} 
    If the existence of negative energy is confirmed, 
    its role in the broader context of cosmology would be a captivating area of inquiry. 
    Understanding how negative energy might influence phenomena like dark energy or the expansion of 
    the universe could revolutionize our understanding of the cosmos.
