\section{Derivation}
\noindent\textbf{Define:}
\begin{enumerate}
    \item $a$ - The distance between two uncharged conductive plates in a vacuum.
    \item The plates lie parallel to the \(xy\)-plane and is orthogonal to \(z\)-axis.
\end{enumerate}

\noindent\textbf{Calculate the Expected Vacuum Energy}

$\langle E \rangle$ represents the expected vacuum energy, 
which is the average $\bar E$ of individual energy states ($E_n$) for all possible states ($n$) in the system.
\begin{align}
    &\langle E \rangle = \sum_{n=1}^{\infty}E_n = \sum_{n=1}^{\infty}\bar{E}
\end{align}

We can express the average energy $\bar E$ as the energy uncertainty of 
a state $\Delta E_n$ divided by the ratio of its existence time $\Delta t_n$ 
to a characteristic timescale $t$.
This timescale $t$ represents the time it takes energy to travel across the gap $a$ between the plates.
\begin{align}
    &t = \frac{a}{c} \\
    &\bar{E} = \Delta E_n\frac{\Delta t_n}{t}
\end{align}

A key concept from the Heisenberg uncertainty principle states that 
the uncertainty energy of a state ($\Delta E_n$) and its corresponding uncertainty in time ($\Delta t_n$) are related by a constant factor ($\hbar/2$)
\begin{align}
    &\Delta E_n \Delta t_n = \frac{\hbar}{2}\\
    &\Delta E_n \frac{\Delta t_n}{t} = \frac{\hbar c }{2 a}\\
    &\langle E \rangle = \sum_{n=1}^{\infty} \frac{\hbar c }{2 a}
\end{align}
\begin{itemize}
    \item \textbf{Summation notation:} Define the expected vacuum energy (denoted by $\langle E \rangle$ ) 
    as the average of individual energy states (represented by $E_n$). 
    Since we're summing over infinitely many states, summation notation is used.
    \item \textbf{Relating energy and time:} The key idea is that the energy uncertainty ($\Delta E_n$) is related 
    to the time uncertainty ($\Delta t_n$) through a constant factor ($\hbar/2$).
    \item \textbf{Calculating energy uncertainty:} Calculate the energy uncertainty for each state ($\Delta E_n$)
     using the wavenumber and the proportionality constant from the uncertainty principle.
    \item \textbf{Deriving time uncertainty ratio:} Calculate the ratio of the time uncertainty for each state ($\Delta t_n$)
     to the total time period ($t$). This ratio is inversely proportional to the energy uncertainty.
    \item \textbf{Summing the expected energy:} This expresses the expected vacuum energy density by summing 
    the product of energy uncertainty and its corresponding time uncertainty ratio for all states, 
    divided by the total area (which will be calculated later). 
    This summation represents the average energy density across all possible quantum states.
\end{itemize}
\noindent\textbf{Calculate the Area}
\par

The total area $A$ is the sum of the areas $A_n$ for each individual state $n$.
The concept behind this summation is that the overall area accessible to 
a particle is determined by considering the allowed areas for each possible quantum state.
\begin{align}
    A = \sum_{n=1}^{\infty}A_n
\end{align}

    The $n$th area $A_n$ relates to the change in length and the change in position.
    \begin{align}
        A_n = L_n^2 = (\frac{a}{\Delta x_n^{x,y} \cdot n^z} \cdot a)^2
    \end{align}

    The wavenumber $k_n$ associated with the $n$th state. It relates to the momentum and wavelength of the particle in that state.
    \begin{align}
        &k_n = \frac{n \pi}{a} \\
        &p_n = \hbar k_n = \frac{n \pi \hbar}{a}
    \end{align}

    This equation calculates the change in position along the x and y directions $\Delta x_n^{x,y}$ for the $n$th state. 
It uses the Heisenberg uncertainty principle, which states that the product of momentum uncertainty and position uncertainty 
has a lower bound.
    \begin{align}
        \Delta x_n^{x, y} = \frac{\hbar/2}{p_n} = \frac{\hbar/2}{n \pi \hbar/a} = \frac{a}{2 n \pi}
    \end{align}
$n^z$ represents the ratio of a single wave in $n$th state passing through the z-axis to the plates.
    \begin{align}
        n^z = \frac{a}{2 n \pi} \cdot \frac{2 \pi}{a} =\frac{1}{n}
    \end{align}
    
Therefore

    \begin{align}
        A_n = (\frac{a}{\Delta x_n^{x,y} \cdot n^z} \cdot a)^2 = 4 n^4 \pi^2 a^2
    \end{align}
    \begin{align}
        A = \sum_{n=1}^{\infty}4 n^4 \pi^2 a^2
    \end{align}

This summation considers all possible quantum states the particle can occupy within the system 
defined by the distance between the plates.
\begin{itemize}
    \item \textbf{Relating area and uncertainty:} The concept is that the area for a particular state is related to 
    the change in length ($L_n$) and the change in position ($\Delta x_n^{x,y}$) along the x and y axes.
    \item \textbf{Defining state variables:} Define the ratio for the $n$th state ($n^z$) 
    and the momentum ($p_n$) associated with that state.
    \item \textbf{Calculating x,y position uncertainty:} Due to the confinement in the z-axis, 
    this calculates the change in position along the x and y directions for the $n$th state ($\Delta x_n^{x,y}$). 
    This is derived using the uncertainty principle and the momentum along those directions.
    \item \textbf{Expressing Area:} The formula for the area ($A_n$) of the $n$th state relates the area to the change in length, 
    change in position along x and y, and the distance between the plates.
    \end{itemize}
\noindent\textbf{Calculate Vacuum Energy on Two Plates}
\begin{align}
    &\frac{\langle E \rangle}{A} = \sum_{n=1}^{\infty}\Delta E_n\frac{\Delta t_n}{t}\frac{1}{A_n} = \sum_{n=1}^{\infty} \frac{\hbar c }{2 a} \cdot \frac{1}{4 n^4 \pi^2 a^2} \nonumber \\
    &= \sum_{n=1}^{\infty} \frac{\hbar c}{8 n^4 \pi^2 a^3} = \frac{\hbar c}{8 \pi^2 a^3} \sum_{n=1}^{\infty} \frac{1}{n^4} \nonumber \\
    &= \frac{\hbar c}{8 \pi^2 a^3} \zeta(4) = \frac{\hbar c}{8 \pi^2 a^3} \cdot \frac{\pi^4}{90} = \frac{\hbar c \pi^2}{720 a^3}
\end{align}
